\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-02-19 write_up/F_changes.tex
Text updates and include test of effectiveness of knowledge parameters

% latex table generated in R 3.5.2 by xtable 1.8-3 package
% Mon Jan 28 16:57:19 2019
\begin{longtable}{rllrrrlllr}
\caption{Fishing mortality effects of the closure scenarios} \\ 
  \hline
scenario & metric & pop & before & after & diff (\%) & timescale & basis & data\_type & resolution \\ 
  \hline
  9 & F & spp\_3 & 1.08 & 0.29 & -73.47 & weekly & high\_pop & real\_pop & 1.00 \\ 
   10 & F & spp\_3 & 1.08 & 0.29 & -72.94 & monthly & high\_pop & real\_pop & 1.00 \\ 
   11 & F & spp\_3 & 1.08 & 0.35 & -68.04 & yearly & high\_pop & real\_pop & 1.00 \\ 
   45 & F & spp\_3 & 1.08 & 0.58 & -46.70 & yearly & high\_pop & commercial & 20.00 \\ 
    1 & F & spp\_3 & 1.08 & 0.58 & -46.21 & weekly & high\_pop & commercial & 1.00 \\ 
   23 & F & spp\_3 & 1.08 & 0.59 & -45.27 & weekly & high\_pop & real\_pop & 5.00 \\ 
    2 & F & spp\_3 & 1.08 & 0.59 & -45.06 & monthly & high\_pop & commercial & 1.00 \\ 
    7 & F & spp\_3 & 1.08 & 0.60 & -44.48 & yearly & high\_pop & survey & 1.00 \\ 
   24 & F & spp\_3 & 1.08 & 0.61 & -43.20 & monthly & high\_pop & real\_pop & 5.00 \\ 
    3 & F & spp\_3 & 1.08 & 0.64 & -40.82 & yearly & high\_pop & commercial & 1.00 \\ 
   25 & F & spp\_3 & 1.08 & 0.65 & -39.94 & yearly & high\_pop & real\_pop & 5.00 \\ 
   17 & F & spp\_3 & 1.08 & 0.67 & -38.11 & yearly & high\_pop & commercial & 5.00 \\ 
   15 & F & spp\_3 & 1.08 & 0.71 & -34.38 & weekly & high\_pop & commercial & 5.00 \\ 
   43 & F & spp\_3 & 1.08 & 0.71 & -34.31 & weekly & high\_pop & commercial & 20.00 \\ 
   16 & F & spp\_3 & 1.08 & 0.73 & -32.58 & monthly & high\_pop & commercial & 5.00 \\ 
   51 & F & spp\_3 & 1.08 & 0.78 & -27.92 & weekly & high\_pop & real\_pop & 20.00 \\ 
   37 & F & spp\_3 & 1.08 & 0.78 & -27.76 & weekly & high\_pop & real\_pop & 10.00 \\ 
   39 & F & spp\_3 & 1.08 & 0.79 & -26.98 & yearly & high\_pop & real\_pop & 10.00 \\ 
   38 & F & spp\_3 & 1.08 & 0.81 & -25.47 & monthly & high\_pop & real\_pop & 10.00 \\ 
   21 & F & spp\_3 & 1.08 & 0.81 & -25.21 & yearly & high\_pop & survey & 5.00 \\ 
   35 & F & spp\_3 & 1.08 & 0.81 & -25.05 & yearly & high\_pop & survey & 10.00 \\ 
   44 & F & spp\_3 & 1.08 & 0.87 & -19.91 & monthly & high\_pop & commercial & 20.00 \\ 
   52 & F & spp\_3 & 1.08 & 0.88 & -18.39 & monthly & high\_pop & real\_pop & 20.00 \\ 
   30 & F & spp\_3 & 1.08 & 0.96 & -11.06 & monthly & high\_pop & commercial & 10.00 \\ 
   29 & F & spp\_3 & 1.08 & 0.98 & -9.80 & weekly & high\_pop & commercial & 10.00 \\ 
   31 & F & spp\_3 & 1.08 & 1.03 & -4.36 & yearly & high\_pop & commercial & 10.00 \\ 
   53 & F & spp\_3 & 1.08 & 1.06 & -1.64 & yearly & high\_pop & real\_pop & 20.00 \\ 
   49 & F & spp\_3 & 1.08 & 1.07 & -1.01 & yearly & high\_pop & survey & 20.00 \\ 
   \hline
\hline
\label{tab:6}
\end{longtable}

>>>>

% latex table generated in R 3.5.2 by xtable 1.8-3 package
% Tue Feb 19 17:00:17 2019
\begin{longtable}{rllrrrlllr}
\caption{Fishing mortality effects of the
     closure scenarios (ordered by most effective first)} \\ 
  \hline
scenario & metric & pop & before & after & diff & timescale & basis & data\_type & resolution \\ 
  \hline
  9 & F & spp\_3 & 1.08 & 0.29 & -73.47 & weekly & high\_pop & real\_pop & 1.00 \\ 
   10 & F & spp\_3 & 1.08 & 0.29 & -72.94 & monthly & high\_pop & real\_pop & 1.00 \\ 
   11 & F & spp\_3 & 1.08 & 0.35 & -68.04 & yearly & high\_pop & real\_pop & 1.00 \\ 
   45 & F & spp\_3 & 1.08 & 0.58 & -46.70 & yearly & high\_pop & commercial & 20.00 \\ 
    1 & F & spp\_3 & 1.08 & 0.58 & -46.21 & weekly & high\_pop & commercial & 1.00 \\ 
   23 & F & spp\_3 & 1.08 & 0.59 & -45.27 & weekly & high\_pop & real\_pop & 5.00 \\ 
    2 & F & spp\_3 & 1.08 & 0.59 & -45.06 & monthly & high\_pop & commercial & 1.00 \\ 
    7 & F & spp\_3 & 1.08 & 0.60 & -44.48 & yearly & high\_pop & survey & 1.00 \\ 
   24 & F & spp\_3 & 1.08 & 0.61 & -43.20 & monthly & high\_pop & real\_pop & 5.00 \\ 
    3 & F & spp\_3 & 1.08 & 0.64 & -40.82 & yearly & high\_pop & commercial & 1.00 \\ 
   25 & F & spp\_3 & 1.08 & 0.65 & -39.94 & yearly & high\_pop & real\_pop & 5.00 \\ 
   17 & F & spp\_3 & 1.08 & 0.67 & -38.11 & yearly & high\_pop & commercial & 5.00 \\ 
   15 & F & spp\_3 & 1.08 & 0.71 & -34.38 & weekly & high\_pop & commercial & 5.00 \\ 
   43 & F & spp\_3 & 1.08 & 0.71 & -34.31 & weekly & high\_pop & commercial & 20.00 \\ 
   16 & F & spp\_3 & 1.08 & 0.73 & -32.58 & monthly & high\_pop & commercial & 5.00 \\ 
   51 & F & spp\_3 & 1.08 & 0.78 & -27.92 & weekly & high\_pop & real\_pop & 20.00 \\ 
   37 & F & spp\_3 & 1.08 & 0.78 & -27.76 & weekly & high\_pop & real\_pop & 10.00 \\ 
   39 & F & spp\_3 & 1.08 & 0.79 & -26.98 & yearly & high\_pop & real\_pop & 10.00 \\ 
   38 & F & spp\_3 & 1.08 & 0.81 & -25.47 & monthly & high\_pop & real\_pop & 10.00 \\ 
   21 & F & spp\_3 & 1.08 & 0.81 & -25.21 & yearly & high\_pop & survey & 5.00 \\ 
   35 & F & spp\_3 & 1.08 & 0.81 & -25.05 & yearly & high\_pop & survey & 10.00 \\ 
   44 & F & spp\_3 & 1.08 & 0.87 & -19.91 & monthly & high\_pop & commercial & 20.00 \\ 
   52 & F & spp\_3 & 1.08 & 0.88 & -18.39 & monthly & high\_pop & real\_pop & 20.00 \\ 
   30 & F & spp\_3 & 1.08 & 0.96 & -11.06 & monthly & high\_pop & commercial & 10.00 \\ 
   29 & F & spp\_3 & 1.08 & 0.98 & -9.80 & weekly & high\_pop & commercial & 10.00 \\ 
   31 & F & spp\_3 & 1.08 & 1.03 & -4.36 & yearly & high\_pop & commercial & 10.00 \\ 
   53 & F & spp\_3 & 1.08 & 1.06 & -1.64 & yearly & high\_pop & real\_pop & 20.00 \\ 
   49 & F & spp\_3 & 1.08 & 1.07 & -1.01 & yearly & high\_pop & survey & 20.00 \\ 
   \hline
\hline
\label{tab:6}
\end{longtable}

### 2019-02-19 write_up/mixfishsim_ecolmod.tex
Text updates and include test of effectiveness of knowledge parameters

\replaced[id = JJ]{Most fisheries}{Fishing} exploit\deleted[id=JJ]{s} a variety 
of spatially and temporally heterogeneous fish populations, using
species-unselective gear that can result in unintended, unwanted catch of low
quota or protected species. Reducing these unwanted catches is crucial for
biological and economic sustainability of `mixed fisheries' and implementation
of an ecosystem approach to fishing. \\

@@

%% the tikz figure
\input{Process_model.tex}

@@

We parametrised the simulation model for four populations with differing
habitat preference\replaced{,}{ and} temperature tolerances (Figures
\ref{S-fig:1}, \ref{S-fig:3}, \ref{S-fig:4}, \ref{S-fig:5}, \ref{S-fig:6},
\ref{S-fig:7}), population demographics and recruitment functions. In addition,
each of the populations has two defined spawning areas which result in the
populations moving towards these areas in given weeks (Figure \ref{S-fig:2})
and population-specific movement rates (Table \ref{tab:1}). The realised
movement of the populations for a number of weeks is shown in Figure
\ref{S-fig:9} while the realised daily fishing mortality are shown in Figure
\ref{S-fig:10}.

@@

The fleets were parametrised to reflect five different characteristic fisheries
with unique exploitation dynamics (Table \ref{tab:2}).  \replaced[id=PD]{By
	setting different catchability parameters ($Q_{fl, p}$) we create
	different targeting preferences between the fleets and hence spatial
	dynamics}{This ensures that different fleets have different spatial
	dynamics, preferentially targeted different fish populations}.  The
stochasticity in the random walk process ensures that within a fleet different
vessels have slightly different spatial distributions based on individual
experience. The step function was parametrised dynamically within the
simulations as the maximum revenue obtainable was not known beforehand. This
was implemented so that vessels take smaller steps where the fishing location
yields in a top quartile of the value experienced in each year (as defined per
fleet in Table \ref{tab:2}). \\

With an increasing probability throughout the simulation fishing locations were
chosen based on experience built up in the same month from previous years and
from past trip fishing success.  'Success' in this context was defined as the
locations where the top 75 \% of expected profit would be found given previous
trips revenue and cost of movement to the new fishing location. This
probability was based on a logistic sigmoid function with a lower asymptote of
0 and upper asymptote of 0.95, and a growth rate which ensures the upper
asymptote (where decisions are mainly based on past knowledge) is reached
$\sim$ halfway through the simulation).  \\

An example of the realised fleet movements for a single vessel during a single
trip are given in Figure \ref{S-fig:11}, while Figure \ref{S-fig:12} shows
multiple trips for a single vessel, \added[id=PD]{Figure} \ref{S-fig:13} the
vessel movements for some trips overlaid on the value field,
\added[id=PD]{Figure} \ref{S-fig:14} shows fishing locations for an entire
fleet of 20 vessels for a single trip, \replaced[id=PD]{and Figure}{while}
\ref{S-fig:15} shows an example of the step function realisation and turning
angles from the correlated random walk.\todo{\added[id=JJ]{Move some of the
	supplementary figures to the manuscript}}

@@

To illustrate the capabilities on \emph{MixFishSim}, we investigate the
influence of the temporal and spatial resolution of different data sources on
the reduction in catches of a population given spatial closures. To do so, we
set up a simulation to run for 50 years based on a 100 X 100 square grid, with
five fleets of 20 vessels each and four fish populations. Fishing takes place
four times a day per vessel and five days a week, while population movement is
every week.\todo{\added[id=JJ]{move to start of methods section}\added[id=PD]{I
		think ecological modelling wants the 'calculations' section
		here..will check}} \\

We allow the simulation to run unrestricted for 30 years\todo{\added[id=JJ]{Is
		there equilibrium after 5 years or still some trend in
		B}\added[id=PD]{Not at equilibrium yet...I need to rerun until
		steady state, looks 20 years. Will update}}, and subsequently
close areas for the last 20 years of the simulation based on data (either
derived from the commercial catches, fisheries-independent survey or the 'real
population' - where the underlying populations assumed to be known perfectly)
used at different spatial and temporal scales. \\

The following steps are undertaken to determine closures:
\todo{\added[id=JJ]{Procedure unclear. Refer to symbols in methods section or
		switch order starting with description of data type
		etc..}\added[id=PD]{Yes, will redo}}
\begin{enumerate}
	\item Extract data source
	\item Aggregate according to resolution
	\item Interpolate across entire area at desired resolution
	\item Close area covering top 5 \% of catch 
\end{enumerate}
In total 56 closure scenarios were run which represent combinations of

@@

The consequences of different spatial aggregations of the data are shown in
Figure \ref{fig:1}, which represents the aggregation of catch from each of the
data sources over a year at different spatial resolutions. \\

The finer spatial grid for the the real population (top left) and commercial
data (top middle) show similar patterns, though there are unsampled gaps in the
commercial data from a lack of fishing activity (particularly in the lower left
part of the sampling domain). The survey data at this spatial resolution shows
very sparse and uninformative information about the spatial distributions of
the populations. The slightly aggregated data on a 5 x 5 grid shows similar
patterns, and while losing some of the spatial detail there remains good
consistency between the 'real population' and the commercial data. Survey data
starts to pick out some of the similar patterns as the other data sources, but
lacks coverage. The spatial catch information on a 10 x 10 and 20 x 20 grid
loses a significant amount of information about the spatial resolutions for all
data sources, and some differences between the commercial and 'real population'
data emerge. \\

Figure \ref{fig:2} shows the consequences of different temporal aggregations of
the data, with 156 weekly (top), 36 monthly (middle) and 3 yearly (bottom)
catch compositions across a 20 x 20 area. \\

As can be seen from the 'real population', the monthly aggregation captures the
major patterns seen in the weekly data, albeit missing more subtle differences.
The yearly data results in a constant catch pattern due to the aggregation
process (sometimes known as an aggregation bias). The commercial data on a
weekly basis shows some of the same patterns as the 'real population', though
the first species (in red) is less well represented and some weeks are missing
catches from the area. The monthly data. The monthly data shows some
consistency between the 'real population' and commercial data for species 2 -
4, though species 1 remains underrepresented. On an annual basis, interestingly
the commercial data underrepresents the first species (in red) while the survey
overrepresents species 1. This is likely due to the biases in commercial
sampling, with the fisheries not targeting the areas where species 1 are
present, and the biases in the survey sampling from overrepresentation of the
spatial distribution. \\

We implemented a spatial closure using the different data sources and spatial
and temporal aggregations as outlined in the protocol in Section 3.4. We used
this to assess the efficacy of a closure in reducing fishing mortality on
species 1, given availability of data and its use at different resolutions in
order to evaluate the trade-offs in data sources. Figure \ref{fig:3} shows the
trend in fishing mortality for each species simulated (columns) given the data
sources (rows), temporal aggregations (colour lines) and spatial aggregations
(linestyles), while Figure \ref{fig:4} shows the change in fishing mortality
from before the closure (average F years 2 - 4) to after the closure (average F
years 8 - 10). \\

@@

\begin{table}[!ht]
	\centering
	\caption{Description of variables for population dynamics sub-module}
	\label{tab: pop_variable}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Population dynamics}}  \\
		\hhline{===}
		\multicolumn{3}{l}{\textit{Delay-difference model}} \\
		\hline
		$B_{c,d}$ & Biomass in cell $c$ and day $d$ & kg \\
		$Z_{c,d}$ & Total mortality in cell $c$ for day $d$ & - \\
		$R_{c, \tilde{y}}$  &Annualy recruited fish in cell &  yr\textsuperscript{-1} \\
		$\rho$ & Brody's growth coefficient & yr\textsuperscript{-1} \\
		$Wt_{R}$ & Weight of a fully recruited fish & kg \\
		$Wt_{R-1}$ & Weight of a pre-recruit fish & kg \\
		$\alpha_{d}$ & Proportion of annually recruited fish recruited
		during day $d$ & - \\
		\hline
		\multicolumn{3}{l}{\textit{Baranov catch equation}} \\
		\hline
		$C_{c,d}$ & Catch from cell $c$ for day $d$ & kg \\
		$F_{c,d}$ & Instantaneous rate of fishing mortality in cell $c$
		on day $d$ & - \\
		$M_{c,d}$ & Instantaneous rate of natural mortality in cell $c$
		on day $d$ & - \\
		$B_{c,d}$ & Biomass in cell $c$ on day $d$ & kg \\
		\hline
		\multicolumn{3}{c}{\textbf{Recruitment dynamics}} \\
		\hhline{===}
		$\tilde{R}_{c,d}$ & is the recruitment in cell $c$ for day $d$ & $d^{-1}$ \\
		$B_{c,d}$ & is the Biomass in cell $c$ for day $d$ & $d^{-1}$ \\
		$\alpha$ & the maximum recruitment rate & kg  \\
		$\beta$ & the biomass required to produce half the maximum rate
		of recruitment & kg \\
		\bottomrule
		\end{tabular}
	\end{table}

\begin{table}[!ht]
	\centering
	\caption{Description of variables for population movement sub-module}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Population movement dynamics}} \\
		\hhline{===}
		\multicolumn{3}{l}{\textit{Habitat model}} \\
		\hline
		a & b & c \\
		\hline
		\multicolumn{3}{l}{\textit{Thermal tolerance}} \\
		\hline
		$T_{c,wk}$ & Temperature for cell in week & $^\circ$C \\
		$\mu_{p}$ & Mean of the thermal tolerance for population & $^\circ$C \\
		$\sigma^{2}_{p}$ & Standard deviation of thermal tolerance for
		the population & $^\circ$C \\
		\hline
		\multicolumn{3}{l}{\textit{Population movement model}} \\
		\hline
		$\lambda$ & decay rate for population movement & - \\
		$Hab^{2}_{c,p}$ & Square of habitat suitability for cell $c$ and
		population $p$ & - \\
		$Tol_{c,p,wk}$ & Thermal tolerance for population $p$ in cell
		$c$ at week $wk$ & - \\
		$d_{IJ}$ & euclidean distance between cell $I$ and cell $J$ & - \\
		\bottomrule
		\end{tabular}
	\end{table}

\begin{table}[!ht]
	\centering
	\caption{Description of variables for fleet dynamics sub-module}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Short-term fleet dynamics}} \\
		\hhline{===}
		$Rev$ & Revenue from fishing tow & \euro \\
		$L_{p}$ & Landings of population $p$ & kg \\
		$Pr_{p}$ & Average price of population $p$ & \euro
		\hspace{0.1cm} kg$^{-1}$ \\
		StepL & Step length for vessel & euclidean distance \\
		Br & Bearing & degrees \\
		$k$ & Concentration parameter for Von mises distribution & - \\
		$\beta_{1}$ & shape parameter for step function & - \\
		$\beta_{2}$ & shape parameter for step function & - \\
		$\beta_{3}$ & shape parameter for step function & - \\
		\bottomrule
	\end{tabular}
\end{table}

\begin{table}[!ht]
\caption{Population dynamics and movement parameter setting}
	\begin{tabular}{ p{4cm } p{2cm} p{2cm} p{2cm} p{2cm}}
	Parameter & Pop 1 & Pop 2 & Pop 3 & Pop 4 \\
	\hline
	Habitat quality & & & \\
	\hline
	Matérn $\nu$ & 1/0.015 & 1/0.05 & 1/0.01 & 1/0.005  \\
	Matérn $\kappa$ & 1 & 2 & 1 & 1  \\
	Anisotropy & 1.5,3,-3,4 & 1,2,-1,2 & 2.5,1,-1,2 & 0.1,2,-1,0.2 \\
	Spawning areas (bound box) & 40,50,40,50; 80,90,60,70 &
	50,60,30,40; 80,90,90,90 & 30,34,10,20; 60,70,20,30 & 50,55,80,85; 30,40,30,40 \\
	Spawning multiplier & 10 & 10 & 10 & 10 \\
	Movement $\lambda$ & 0.1 & 0.1 & 0.1 & 0.1 \\
	\hline
	Population dynamics & & & & \\
	\hline
	Starting Biomass & 1e5 & 2e5 & 1e5 & 1e4 \\
	Beverton-Holt Recruit 'a' & 6 & 27 & 18 & 0.3  \\
	Beverton-Holt Recruit 'b' & 4 & 4 & 11 & 0.5 \\
	Beverton-Holt Recruit $\sigma^2$ & 0.7 & 0.6 & 0.7 & 0.6 \\
	Recruit week & 13-16 & 12-16 & 14-16 & 16-20 \\
	Spawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
	$K$ & 0.3 & 0.3 & 0.3 & 0.3 \\
	$wt$ & 1 & 1 & 1 & 1 \\
	$wt_{d-1}$ & 0.1 & 0.1 & 0.1 & 0.1 \\
	M (annual) & 0.2 & 0.1 & 0.2 & 0.1 \\
	\hline
	Movement dynamics & & & & \\
	\hline
	$\mu$ & 12 & 15 & 17 & 14 \\
	$\sigma^2$ & 8 & 9 & 7 & 10 \\
	\hline
\end{tabular}
\label{tab:1}
\end{table}

\begin{table}[!ht]
\caption{Fleet dynamics parameter setting}
\begin{tabular}{ p{4cm } p{1cm} p{1cm} p{1cm} p{1cm} p{1cm}}
	\hline
	Parameter & Fleet 1 & Fleet 2 & Fleet 3 & Fleet 4 & Fleet 5 \\
	\hline
	Targeting preferences &&&& \\
	\hline
	Price Pop1 & 100 & 100 & 100 & 100 & 100 \\
	Price Pop2 & 200 & 200 & 200 & 200 & 200 \\
	Price Pop3 & 350 & 350 & 350 & 350 & 350 \\
	Price Pop4 & 600 & 600 & 600 & 600 & 600 \\
	$Q$ Pop1 & 0.01 & 0.02 & 0.02 & 0.01 & 0.01 \\
	$Q$ Pop2 & 0.02 & 0.01 & 0.02 & 0.01 & 0.03\\
	$Q$ Pop3 & 0.01 & 0.02 & 0.02 & 0.01 & 0.02 \\
	$Q$ Pop4 & 0.02 & 0.01 & 0.02 & 0.05 & 0.01 \\
	\hline
	Exploitation dynamics &&&& \\
	\hline
	step function $\beta_1$ & 1 & 2 & 1 & 2 & 3 \\
	step function $\beta_2$ & 10 & 15 & 8 & 12 & 7 \\
	step function $\beta_3$ & Q90 & Q90 & Q85 & Q90 & Q80 \\
	step function $rate$ & 20 & 30 & 25 & 35 & 20 \\
	Past Knowledge & T & T & T & T & T \\
	Past Year \& Month & T & T & T & T & T \\
	Past Trip & T & T & T & T & T \\
	Threshold & 0.7 & 0.7 & 0.7 & 0.7 & 0.7 \\
	Fuel Cost & 3 & 2 & 5 & 2 & 1 \\
	\hline
\end{tabular}
\label{tab:2}
\end{table}

\newpage
\input{F_changes.tex}

%%%% figures
\begin{figure}[!ht]
	\includegraphics[width =\linewidth]{../analysis/Data_Aggregation_space}
	\caption{Data aggregation at different spatial resolutions}
	\label{fig:1}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/Data_Aggregation_time}
	\caption{Data aggregation at different temporal resolutions}
	\label{fig:2}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/F_trendsREV}
	\caption{Comparison of closure scenarios - F trends}
	\label{fig:3}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width =\linewidth]{../analysis/Overview_plot_highPopRev}
	\caption{Comparison of closure scenarios}
	\label{fig:4}
\end{figure}

@@

>>>>

\replaced[id = JJ]{Most fisheries}{Fishing} exploit\deleted[id=JJ]{s} a variety 
of spatially and temporally heterogeneous fish populations using
species-unselective gear that can result in unintended, unwanted catch of low
quota or protected species. Reducing these unwanted catches is crucial for
biological and economic sustainability of `mixed fisheries' and implementation
of an ecosystem approach to fishing. \\

@@

%% the tikz figure
\clearpage
\input{Process_model.tex}

@@

We parametrised the simulation model for four populations with different
population demographics; growth rates, natural mortality and recruitment
functions (Table \ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and
temperature tolerances (Figures \ref{S-fig:3}, \ref{S-fig:4}) were unique to
each population resulting in differently weekly distribution patterns (Figures
\ref{S-fig:5}-\ref{S-fig:7}). In addition, each of the populations has two
defined spawning areas which result in the populations moving towards these
areas in pre-defined weeks (Figure \ref{S-fig:2}) with population-specific
movement rates (Table \ref{tab:1}). The realised movement of the populations
for a number of weeks is shown in Figure \ref{S-fig:9} while the realised daily
fishing mortality are shown in Figure \ref{S-fig:10}.

@@

The fleets were parametrised to reflect five different characteristic fisheries
with unique exploitation dynamics (Table \ref{tab:2}).  \replaced[id=PD]{By
	setting different catchability parameters ($Q_{fl, p}$) we create
	different targeting preferences between the fleets and hence spatial
	dynamics}{This ensures that different fleets have different spatial
	dynamics, preferentially targeted different fish populations}.  The
stochasticity in the random walk process ensures that within a fleet different
vessels have slightly different spatial distributions based on individual
experience. The step function was parametrised dynamically within the
simulations as the maximum revenue obtainable was not known beforehand. This
was implemented so that vessels take smaller steps when fishing at a location
yields landings value which is in the top 90th percentile of the value
experienced in that year (as defined per fleet in Table \ref{tab:2}). \\

With increasing probability throughout the simulation, fishing locations were
chosen based on experience of profitable catches built up in the same month
from previous years and from the previous trip. 'Profitable' in this context
was defined as the locations where the top 70 \% of expected profit would be
found given previous trips revenue and cost of movement to the new fishing
location.  This probability was based on a logistic sigmoid function with a
lower asymptote of 0 and upper asymptote of 0.95, and a growth rate which
ensures the upper asymptote (where decisions are mainly based on past
knowledge) is reached $\sim$ halfway through the simulation.  \\

An example of the realised fleet movements for a single vessel during a single
trip are given in Figure \ref{S-fig:11}, while Figure \ref{S-fig:12} shows
multiple trips for a single vessel, \added[id=PD]{Figure} \ref{S-fig:13} the
vessel movements for several trips overlaid on the value field (sum of the
population densities $\times$ price), \added[id=PD]{Figure} \ref{S-fig:14} shows
fishing locations for an entire fleet of 20 vessels for a single trip,
\replaced[id=PD]{and Figure}{while} \ref{S-fig:15} shows an example of the step
function realisation and turning angles from the correlated random
walk.\todo{\added[id=JJ]{Move some of the supplementary figures to the
		manuscript}}

@@

To illustrate the capabilities on \emph{MixFishSim}, we investigate the
influence of the temporal and spatial resolution of different data sources on
the reduction in catches of a population given spatial closures. To do so, we
set up a simulation to run for 50 years based on a 100 $\times$ 100 square
grid, with five fleets of 20 vessels each and four fish populations. Fishing
takes place four times a day per vessel and five days a week, while population
movement is every week.\todo{\added[id=JJ]{move to start of methods
		section}\added[id=PD]{I think ecological modelling wants the
		'calculations' section here..will check}} \\

We allow the simulation to run unrestricted for 30 years\todo{\added[id=JJ]{Is
		there equilibrium after 5 years or still some trend in B?
	}\added[id=PD]{I have rerun to ensure some steady state dynamics}},
then implement spatial closed areas for the last 20 years of the simulation
based on data (either derived from the commercial catches,
fisheries-independent survey or the 'real population') used at different
spatial and temporal scales. \\

The following steps are undertaken to determine closures:
\todo{\added[id=JJ]{Procedure unclear. Refer to symbols in methods section or
		switch order starting with description of data type
		etc..}\added[id=PD]{Yes, will redo}}
\begin{enumerate}
	\item Extract data source
	\item Aggregate according to desired spatial and temporal resolution
	\item Interpolate across entire area at desired resolution
	\item Close area covering top 5 \% of catch 
\end{enumerate}
In total 56 closure scenarios were run which represent combinations of:

@@

The consequences of different spatial aggregations of the data are shown in
Figure \ref{fig:1}, which represents the aggregation of catch from each of the
data sources over a ten year period (to average seasonal patterns) at different
spatial resolutions. \\

The finer spatial grid for the real population (top left) and commercial data
(top middle) show similar patterns, though there are unsampled gaps in the
commercial data from a lack of fishing activity (particularly in the lower left
part of the sampling domain). The survey data at this spatial resolution shows
very sparse information about the spatial distributions of the populations. The
slightly aggregated data on a 5 x 5 grid shows similar patterns, and while
losing some of the spatial detail there remains good consistency between the
'real population' and the commercial data. Survey data starts to pick out some
of the similar patterns as the other data sources, but lacks coverage. The
spatial catch information on a 10 x 10 and 20 x 20 grid loses a significant
amount of information about the spatial resolutions for all data sources, and
some differences between the survey, commercial and 'real population' data
emerge. \\

Figure \ref{fig:2} shows the consequences of different temporal aggregations of
the data over a three year period, with 156 weekly (top), 36 monthly (middle)
and 3 yearly (bottom) catch compositions from across an aggregated 20 x 20
area. \\

As can be seen by comparison to the 'real population', the monthly aggregation
captures the major patterns seen in the weekly data, albeit missing more subtle
differences. The yearly data results in a constant catch pattern due to the
aggregation process (sometimes known as an aggregation bias). The commercial
data on a weekly basis shows some of the same patterns as the 'real
population', though the first species (in red) is less well represented and
some weeks are missing catches from the area. The monthly data. The monthly
data shows some consistency between the 'real population' and commercial data
for species 2 - 4, though species 1 remains under-represented. On an annual
basis, interestingly the commercial data under represents the first species (in
red) while the survey over represents species 1. This is likely due to the
biases in commercial sampling, with the fisheries not targeting the areas where
species 1 are present, and the biases in the survey sampling from over
representation of the spatial distribution. \\

We implemented a spatial closure using the different data sources and spatial
and temporal aggregations as outlined in the protocol in Section 3.4. We used
this to assess the efficacy of a closure in reducing fishing mortality on
species 1, given availability of data and its use at different resolutions in
order to evaluate the trade-offs in data sources. Figure \ref{fig:3} shows the
trend in fishing mortality for each species simulated (columns) given the data
sources (rows), temporal aggregations (colour lines) and spatial aggregations
(line-styles), while Figure \ref{fig:4} shows the change in fishing mortality
from before the closure (year 29) to after the closure (year 50). \\

@@

@@

\input{parameter_tables.tex}

\clearpage
\footnotesize
\input{F_changes.tex}

\clearpage
\footnotesize
\input{F_changes_ratio.tex}

%%%% figures
\begin{figure}[!ht]
	\includegraphics[width =\linewidth]{../analysis/Data_Aggregation_space}
	\caption{Data aggregation at different spatial resolutions over a
		ten year period}
	\label{fig:1}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/Data_Aggregation_time}
	\caption{Data aggregation at different temporal resolutions over a
		three year period}
	\label{fig:2}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/F_trendsREV}
	\caption{Comparison of closure scenarios - Fishing mortality trends.
		Only the scenarios based on high catch rates of population 3
		are shown.}
	\label{fig:3}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width =\linewidth]{../analysis/Overview_plot_highPopRev}
	\caption{Comparison of closure scenarios. Points indicate the
		difference between the fishing mortality pre-closure (year 29)
		and post-closure (year 50) for population 3. Only the scenarios
		based on high catch rates of population 3 are shown.}
	\label{fig:4}
\end{figure}
